Heart stroke-volume variability in a murine model for heart failure with reduced ejection fraction

### 2022-12-13 Manuscript/manuscript.tex
$
update

@@

>>>>

\subsection{Poincairé Plots}

Heart rate variability has been measured using a variety of techniques. The majority of them are based on the notion of signal stationarity. However, the heart rate's inherently nonstationary nature---which undergoes continuous physiological change to adapt to outside stimuli---presents a significant challenge that could lead to inaccurate results. Although a number of signal preprocessing methodologies have been suggested to address these problems, nonlinear analysis-based strategies are frequently used and seem to produce reliable result. One of them that is used in different scientific domains is the Poincairé plot.

@@

\begin{figure}
\includegraphics[width=4in]{model.pdf}
\caption{Scematic representation of the model}
\label{fig:model}
\end{figure}
